FCST

### 2021-02-24 analysis/chapters/forecast_20181122.Rmd
Arreglo figura de observaciones de superficie

```{r}
# files <- Sys.glob(paste0(derived_data, "/interp_obs/2018112206/interp*"))
# 
# obs <- purrr::map(files, function(f) {
#   print(f)
#   read_rds(f) %>% 
#     .[, id := 1:.N, by = ens] %>% 
#     .[, fcst_exp := "2018112206"] %>% 
#     .[, exp := NULL] %>% 
#     melt(measure.vars = c("E4", "E5", "E6", "E7"), 
#          variable.name = "exp",
#          value.name = "fcst") %>% 
#     .[, ":="(obs = if_else(usage.flag == 1, obs, NA_real_),
#              fcst = if_else(usage.flag == 1, fcst, NA_real_))] %>% 
#     .[, c(list(obs = mean(obs, na.rm = TRUE),
#                fcst = mean(fcst, na.rm = TRUE)),
#           .SD[ens == 1]), by = .(id, exp), .SDcols = -c("obs", "fcst")] %>% 
#     .[usage.flag == 1]
#   
# }) %>% 
#   rbindlist()

@@

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "bias"] %>% 
  ggplot(aes(date, value)) +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```

>>>>

```{r}
# files <- Sys.glob(paste0(derived_data, "/interp_obs/2018112200/interp*"))
# 
# obs <- purrr::map(files, function(f) {
#   print(f)
#   read_rds(f) %>%
#     .[, id := 1:.N, by = ens] %>%
#     .[, fcst_exp := "2018112200"] %>%
#     .[, exp := NULL] %>%
#     melt(measure.vars = c("E4", "E5", "E6", "E7"),
#          variable.name = "exp",
#          value.name = "fcst") %>%
#     .[, ":="(obs = if_else(usage.flag == 1, obs, NA_real_),
#              fcst = if_else(usage.flag == 1, fcst, NA_real_))] %>%
#     .[, c(list(obs = mean(obs, na.rm = TRUE),
#                fcst = mean(fcst, na.rm = TRUE)),
#           .SD[ens == 1]), by = .(id, exp), .SDcols = -c("obs", "fcst")] %>%
#     .[usage.flag == 1]
# 
# }) %>%
#   rbindlist()

@@

rbind(obs_00, obs_06) %>% 
  .[usage.flag == 1] %>% 
  .[, .(rmse = sqrt(mean((obs - fcst)^2, na.rm = TRUE)),
        bias = mean(obs -  fcst, na.rm = TRUE)), by = .(var, date, exp, fcst_exp)] %>% 
  melt(measure.vars = c("rmse", "bias"), variable.name = "estadistico") %>% 
  .[estadistico == "bias"] %>% 
  ggplot(aes(date, value)) +
  geom_hline(yintercept = 0, color = "grey60") +
  geom_line(aes(color = exp, linetype = fcst_exp)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  scale_date() +
  labs(subtitle = "BIAS", x = NULL, y = NULL, linetype = NULL, color = NULL) +
  facet_wrap(~ var, scales = "free_y") +
  theme_minimal()
```
